---
title: "R Notebook"
output:
  word_document: default
  pdf_document:
    latex_engine: xelatex
  html_notebook: default
always_allow_html: yes
---

```{r setup, include=FALSE}

# This chunk shows/hides the code in your final report. When echo = TRUE, the code
# is shown in the report. When echo = FALSE, the code is hidden from the final report.
# We would like to see your code, so please leave the setting as is during the course.
# This chunk will not show up in your reports, so you can safely ignore its existence.

knitr::opts_chunk$set(echo = TRUE)

```


The following is your first chunk to start with. Remember, you can add chunks using the menu
above (Insert -> R) or using the keyboard shortcut Ctrl+Alt+I. A good practice is to use
different code chunks to answer different questions. You can delete this comment if you like.

Other useful keyboard shortcuts include Alt- for the assignment operator, and Ctrl+Shift+M
for the pipe operator. You can delete these reminders if you don't want them in your report.


```{r}
setwd("/Users/shruthinair/Desktop/Lumos/DM") #Don't forget to set your working directory before you start!

library("tidyverse")
library("tidymodels")
library("plotly")
library("skimr")
```
```{r}
dfbOrg <-
read_csv("/Users/shruthinair/Desktop/Lumos/DM/Data/assignment2BikeShare.csv")
```
```{r}
skim(dfbOrg)
```

Question 1:
a. Create additional variables:

```{r}
dfbOrg <- dfbOrg %>%
  mutate(COUNT = CASUAL + REGISTERED) %>%
  mutate(MONTH = months(DATE))

```

b. Scale:

```{r}
dfbStd <- dfbOrg %>%
   mutate_at(c(5:8), funs(c(scale(.))))
```

Question 2:

```{r}
fitAll <-
  lm(formula = COUNT ~ ., data = dfbStd)
summary(fitAll)
```
```{r}
plot(fitAll)
```


Question 3:

a. Adding BADWEATHER:
```{r}
dfbOrg <- dfbOrg %>%
  mutate(BADWEATHER = ifelse(WEATHERSIT == 3 | WEATHERSIT == 4, "YES", "NO"))
```

b. Scatterplot:
```{r}
dfbOrg %>%
ggplot(mapping = aes(x=ATEMP,y=COUNT, color =BADWEATHER)) + geom_point()
```

c: Scatterplots:
```{r}
dfbOrg %>%
ggplot(mapping = aes(x=ATEMP,y=CASUAL, color =BADWEATHER)) + geom_point()

```

```{r}
dfbOrg %>%
ggplot(mapping = aes(x=ATEMP,y=REGISTERED, color =BADWEATHER)) + geom_point()
```
Question 3 (iv):

```{r}
dfbOrg %>%
ggplot(mapping = aes(x=ATEMP,y=COUNT)) + geom_point() + geom_smooth()
```

Question 4:
```{r}
fitCount <-
  lm(formula = COUNT ~ MONTH + WEEKDAY + BADWEATHER + TEMP + ATEMP + HUMIDITY, data = dfbOrg)
summary(fitCount)
```

Question 5:
```{r}
plot(fitCount)
```

Heteroskedasticity found. (Plot)

```{r}
car::vif(fitCount)
```
```{r}
fitCountMod <-
  lm(formula = COUNT ~ WEEKDAY + MONTH + ATEMP + BADWEATHER + HUMIDITY + ATEMP*BADWEATHER, data = dfbOrg)
summary(fitCountMod) 
```

```{r}
plot(fitCountMod)
```

```{r}
car::vif(fitCountMod)
```

Question 6:
a.
```{r}
fitBadWt <-
  lm(formula = COUNT ~ BADWEATHER, data = dfbOrg)
summary(fitBadWt)
```

c. 
```{r}
fitBadWtWeekday <-
  lm(formula = COUNT ~ BADWEATHER + WEEKDAY + BADWEATHER*WEEKDAY, data = dfbOrg)
summary(fitBadWtWeekday)
```

Question 7:
a
```{r}
set.seed(333)
```

b
```{r}
dfbTrain <- dfbOrg %>% sample_frac(0.8)
dfbTest <- setdiff(dfbOrg, dfbTrain)
```

c
```{r}
fitOrg <-
  lm(formula = COUNT ~ WEEKDAY + MONTH + ATEMP + BADWEATHER + HUMIDITY + ATEMP*BADWEATHER, data = dfbTrain)
summary(fitOrg)
```

```{r}
resultsOrg <- dfbTest %>%
  			mutate(PREDICTEDCOUNT = predict(fitOrg, dfbTest))
resultsOrg
```

```{r}
performance <- metric_set(rmse, mae)
performance(resultsOrg, truth=COUNT, estimate=PREDICTEDCOUNT)
```

```{r}
fitNew <-
  lm(formula = COUNT ~ WEEKDAY + MONTH + ATEMP + BADWEATHER + HUMIDITY + WINDSPEED + ATEMP*BADWEATHER, data = dfbTrain)
summary(fitNew)
```

```{r}
resultsNew <- dfbTest %>%
 mutate(PREDICTEDCOUNT = predict(fitNew, dfbTest))
resultsNew
```

```{r}
performance <- metric_set(rmse, mae)
performance(resultsNew, truth=COUNT, estimate=PREDICTEDCOUNT)
```

Question 8:
Model 1:

```{r}
dfbOrgTs <- dfbOrg %>%
  mutate(YEAR = lubridate::year(DATE))
```


```{r}
dfbTrainTs <- dfbOrgTs %>% filter( YEAR == 2011)
dfbTestTs <- setdiff(dfbOrgTs, dfbTrainTs)
```

```{r}
fitOrgTs <-
  lm(formula = COUNT ~ WEEKDAY + MONTH + ATEMP + BADWEATHER + HUMIDITY + ATEMP*BADWEATHER, data = dfbTrainTs)
summary(fitOrgTs)
```

```{r}
resultsTs <- dfbTestTs %>%
  			mutate(PREDICTEDCOUNT = predict(fitOrg, dfbTestTs))
resultsTs
```

```{r}
performance <- metric_set(rmse, mae)
performance(resultsTs, truth=COUNT, estimate=PREDICTEDCOUNT)
```

Model 2:

```{r}
dfbTrainTs1 <- dfbOrgTs %>%
  filter("2011-01-01" <= DATE & DATE < "2012-06-01")
dfbTestTs1 <- dplyr::setdiff(dfbOrgTs, dfbTrainTs1)
```


```{r}
fitNewTs1 <- lm(COUNT ~ MONTH + WEEKDAY + BADWEATHER*ATEMP + HUMIDITY + HOLIDAY, data = dfbTrainTs1)
summary(fitNewTs1)
```

```{r}

resultsNewTs1 <- dfbTestTs1 %>%
  			mutate(predictedCount = predict(fitNewTs1, dfbTestTs1))

resultsNewTs1

```
```{r}

performanceB <- metric_set(rmse, mae)
performanceB(resultsNewTs1, truth = COUNT, estimate = predictedCount)

```

